AN EFFICIENT LOCALIZED MODEL ORDER REDUCTION FRAMEWORK FOR THE SHAPE OPTIMIZATION OF ADDITIVELY MANUFACTURED LATTICE STRUCTURES\break ECCOMAS CONGRESS 2024

### 2024-08-28 paper/paper.tex
add gradientenbeton image

\graphicspath{{./img/}}

@@

\section{NUMERICAL EXPERIMENTS} % (fold)
\label{sec:numerical experiments}

\begin{itemize}
    \item general stuff like FE cell type and degree
    \item software: dolfinx version 0.8.0
    \item PC hardware?
\end{itemize}

@@

\subsection{Graded concrete slab} % (fold)
\label{sub:Graded concrete slab}

>>>>

\urldef{\gradientenbetonurl}\url{https://gradientenbeton.eu/}
\graphicspath{{./img/}}

@@

\section{NUMERICAL EXPERIMENTS} % (fold)
\label{sec:numerical experiments}
The proposed methodology to construct the ROM is evaluated based on the example of a graded concrete slab. In~\cref{sub:Projection error study}, the approximation quality of the local spaces is accessed by studying the projection error. The ROM is validated against the FOM (\cref{sub:Reduced order model validation}) and the solution of a shape optimization problem is presented in~\cref{sub:Shape optimization}.
\comment[id=pd]{TODO: remove these sentences in case the article is too long.}

@@

\subsection{Graded concrete slab} % (fold)
\label{sub:Graded concrete slab}
The numerical example investigated here is motivated by \textit{graded concrete} in which voids are created by inserting hollow bodies into the concrete formwork with the goal of mass reduction, see~\cref{fig:gradientenbeton}.
The problem is simplified and we consider a two dimensional beam under plane stress conditions as shown in~\cref{fig:beam_sketch}.

\begin{figure}
    \begin{center}
        \includegraphics[keepaspectratio,height=4cm]{gradientenbeton_formwork.jpg}
    \end{center}
    \caption{Formwork for a graded concrete slab. Weight savings are achieved by placing hollow spheres along a structured grid inside the formwork. Source:\gradientenbetonurl.}\label{fig:gradientenbeton}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.95\textwidth]{example-image}
    \end{center}
    \caption{}\label{fig:beam_sketch}
\end{figure}
